### 2020-02-08 README.Rmd
Implemented a rudimentary lock system.
Added use_frex_words argument, fully compatible with Chang et al. fix #2

After the coding, you can look at the model precision by printing the oolong test.

```{r, eval = FALSE}
oolong_test
```

@@

Create the oolong test object with the corpus used for training the topic model will generate topic intrusion test cases.

>>>>

After the coding, you need to first finalize the test. Then, you can look at the model precision by printing the oolong test.

```{r, eval = FALSE}
oolong_test$finalize()
oolong_test
```

@@

Creating the oolong test object with the corpus used for training the topic model will generate topic intrusion test cases.
